A Switching Planner for Combined Task and Observation Planning

### 2010-11-23 code/subarchitectures/planner.sa/trunk/src/latex/ICAPS-2011/switching.tex
typos

\[
\begin{array}{c}
\actions(.8,(=(\pp{is-in}~\pp{box})\pp{office}));\\
(pp{reportlook-for-object}~\pp{R2D2}~\pp{box}~\pp{office});\\
(\pp{report-is-in}~\pp{box}~\pp{office})
\end{array}
\]

>>>>

\[
\begin{array}{l}
\actions(.8;(=(\pp{is-in}~\pp{box})\pp{office}));\\
(\pp{look-for-object}~\pp{R2D2}~\pp{box}~\pp{office});\\
(\pp{report-is-in}~\pp{box}~\pp{office})
\end{array}
\]
